---
title: "Coursera Statistical Inference Course Project Part_2"
author: "ZiadAbdelnabi"
date: "7/4/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
In part 2 of this this project we are performing basic inferential data analysis using the ToothGrowth data in the R datasets package.


## Part 2: Basic Inferential Data Analysis Instructions
Now in the second portion of the project, we’re going to analyze the ToothGrowth data in the R datasets package.

### 1.Load the ToothGrowth data and perform some basic exploratory data analysis

**For this analysis, the following R package is needed `ggplot2`**
```{r load-packages, message = FALSE}
library(ggplot2)
```

**Load the ToothGrowth data **
```{r loaddata}
library(datasets)
data(ToothGrowth)
```


### 2. Provide a basic summary of the data and perform some basic exploratory data analysis
```{r summarystats}
str(ToothGrowth)
head(ToothGrowth)
summary(ToothGrowth)

# Plot histogram of the numerical len variable to view the distribution
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp)) +
    geom_bar(stat="identity") +
    facet_grid(. ~ supp) +
    xlab("Dose(mg)") +
    ylab("Tooth length")
```



### 3. Hypothesis tests to compare tooth growth by supp and dose. 
(Only use the techniques from class, even if there’s other approaches worth considering)

```{r}
hypoth1 <- t.test(len ~ supp, data = ToothGrowth)
hypoth1$conf.int

hypoth1$p.value

hypoth2<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 0.5))
hypoth2$conf.int

hypoth2$p.value

hypoth3<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 1))
hypoth3$conf.int

hypoth3$p.value

hypoth4<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 2))
hypoth4$conf.int

hypoth4$p.value

```


## Conclusions
OJ ensures more tooth growth than VC for dosages 0.5 & 1.0. OJ and VC givesthe same amount of tooth growth for dose amount 2.0 mg/day. For the entire trail we cannot conclude OJ is more effective that VC for all scenarios.













